E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-11 paper.tex
finished adding all chapters, editing left

	\subsection{Tables}
	Because tables cannot be split across pages, the best
	placement for them is typically the top of the page
	nearest their initial cite.  To
	ensure this proper ``floating'' placement of tables, use the
	environment \textbf{table} to enclose the table's contents and
	the table caption.  The contents of the table itself must go
	in the \textbf{tabular} environment, to
	be aligned properly in rows and columns, with the desired
	horizontal and vertical rules.  Again, detailed instructions
	on \textbf{tabular} material
	is found in the \textit{\LaTeX\ User's Guide}.

	Immediately following this sentence is the point at which
	Table 1 is included in the input file; compare the
	placement of the table here with the table in the printed
	dvi output of this document.

	\begin{table}
		\centering
		\caption{Frequency of Special Characters}
		\begin{tabular}{|c|c|l|} \hline
			Non-English or Math&Frequency&Comments\\ \hline
			\O & 1 in 1,000& For Swedish names\\ \hline
			$\pi$ & 1 in 5& Common in math\\ \hline
			\$ & 4 in 5 & Used in business\\ \hline
			$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
			\hline\end{tabular}
	\end{table}

	To set a wider table, which takes up the whole width of
	the page's live area, use the environment
	\textbf{table*} to enclose the table's contents and
	the table caption.  As with a single-column table, this wide
	table will ``float" to a location deemed more desirable.
	Immediately following this sentence is the point at which
	Table 2 is included in the input file; again, it is
	instructive to compare the placement of the
	table here with the table in the printed dvi
	output of this document.

	\begin{table*}
		\centering
		\caption{Some Typical Commands}
		\begin{tabular}{|c|c|l|} \hline
			Command&A Number&Comments\\ \hline
			\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
			\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
			\texttt{{\char'134}table}& 300 & For tables\\ \hline
			\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
	\end{table*}
	% end the environment with {table*}, NOTE not {table}!

	\subsection{Figures}
	Like tables, figures cannot be split across pages; the
	best placement for them
	is typically the top or the bottom of the page nearest
	their initial cite.  To ensure this proper ``floating'' placement
	of figures, use the environment
	\textbf{figure} to enclose the figure and its caption.

	This sample document contains examples of \textbf{.eps} files to be
	displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
	\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
	\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
	each of these is found in the \textit{Author's Guide}.

	\begin{figure}
		\centering
		%\includegraphics{System/fuzzer_design}
		\caption{A sample black and white graphic.}
	\end{figure}

	\begin{figure}
		\centering
		%\includegraphics[height=1in, width=1in]{fly.eps}
		\caption{A sample black and white graphic
			that has been resized with the \texttt{includegraphics} command.}
	\end{figure}

	As was the case with tables, you may want a figure
	that spans two columns.  To do this, and still to
	ensure proper ``floating'' placement of tables, use the environment
	\textbf{figure*} to enclose the figure and its caption.
	and don't forget to end the environment with
	{figure*}, not {figure}!

	\begin{figure*}
		\centering
		%\includegraphics{flies.eps}
		\caption{A sample black and white graphic
			that needs to span two columns of text.}
	\end{figure*}

	\subsection{Theorem-like Constructs}
	Other common constructs that may occur in your article are
	the forms for logical constructs like theorems, axioms,
	corollaries and proofs.  There are
	two forms, one produced by the
	command \texttt{{\char'134}newtheorem} and the
	other by the command \texttt{{\char'134}newdef}; perhaps
	the clearest and easiest way to distinguish them is
	to compare the two in the output of this sample document:

	This uses the \textbf{theorem} environment, created by
	the\linebreak\texttt{{\char'134}newtheorem} command:
	\newtheorem{theorem}{Theorem}
	\begin{theorem}
		Let $f$ be continuous on $[a,b]$.  If $G$ is
		an antiderivative for $f$ on $[a,b]$, then
		\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
	\end{theorem}

	The other uses the \textbf{definition} environment, created
	by the \texttt{{\char'134}newdef} command:
	\newdef{definition}{Definition}
	\begin{definition}
		If $z$ is irrational, then by $e^z$ we mean the
		unique number which has
		logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
	\end{definition}

	Two lists of constructs that use one of these
	forms is given in the
	\textit{Author's  Guidelines}.

	There is one other similar construct environment, which is
	already set up
	for you; i.e. you must \textit{not} use
	a \texttt{{\char'134}newdef} command to
	create it: the \textbf{proof} environment.  Here
	is a example of its use:
	\begin{proof}
		Suppose on the contrary there exists a real number $L$ such that
		\begin{displaymath}
		\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
		\end{displaymath}
		Then
		\begin{displaymath}
		l=\lim_{x\rightarrow c} f(x)
		= \lim_{x\rightarrow c}
		\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
		= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
		\frac{f(x)}{g(x)} = 0\cdot L = 0,
		\end{displaymath}
		which contradicts our assumption that $l\neq 0$.
	\end{proof}

	Complete rules about using these environments and using the
	two different creation commands are in the
	\textit{Author's Guide}; please consult it for more
	detailed instructions.  If you need to use another construct,
	not listed therein, which you want to have the same
	formatting as the Theorem
	or the Definition\cite{salas:calculus} shown above,
	use the \texttt{{\char'134}newtheorem} or the
	\texttt{{\char'134}newdef} command,
	respectively, to create it.

	\subsection*{A {\secit Caveat} for the \TeX\ Expert}
	Because you have just been given permission to
	use the \texttt{{\char'134}newdef} command to create a
	new form, you might think you can
	use \TeX's \texttt{{\char'134}def} to create a
	new command: \textit{Please refrain from doing this!}
	Remember that your \LaTeX\ source code is primarily intended
	to create camera-ready copy, but may be converted
	to other forms -- e.g. HTML. If you inadvertently omit
	some or all of the \texttt{{\char'134}def}s recompilation will
	be, to say the least, problematic.

	\section{Conclusions}
	This paragraph will end the body of this sample document.
	Remember that you might still have Acknowledgments or
	Appendices; brief samples of these
	follow.  There is still the Bibliography to deal with; and
	we will make a disclaimer about that here: with the exception
	of the reference to the \LaTeX\ book, the citations in
	this paper are to articles which have nothing to
	do with the present subject and are used as
	examples only.
	%\end{document}  % This is where a 'short' article might terminate

	%ACKNOWLEDGMENTS are optional
	\section{Acknowledgments}
	This section is optional; it is a location for you
	to acknowledge grants, funding, editing assistance and
	what have you.  In the present case, for example, the
	authors would like to thank Gerald Murray of ACM for
	his help in codifying this \textit{Author's Guide}
	and the \textbf{.cls} and \textbf{.tex} files that it describes.

	%
	% The following two commands are all you need in the
	% initial runs of your .tex file to
	% produce the bibliography for the citations in your paper.
	\bibliographystyle{abbrv}
	\bibliography{biblio}  
	% You must have a proper ".bib" file
	%  and remember to run:
	% latex bibtex latex latex
	% to resolve all references
	%
	% ACM needs 'a single self-contained file'!
	%
	%APPENDICES are optional
	%\balancecolumns
	\appendix
	%Appendix A
	\section{Headings in Appendices}
	The rules about hierarchical headings discussed above for
	the body of the article are different in the appendices.
	In the \textbf{appendix} environment, the command
	\textbf{section} is used to
	indicate the start of each Appendix, with alphabetic order
	designation (i.e. the first is A, the second B, etc.) and
	a title (if you include one).  So, if you need
	hierarchical structure
	\textit{within} an Appendix, start with \textbf{subsection} as the
	highest level. Here is an outline of the body of this
	document in Appendix-appropriate form:
	\subsection{Introduction}
	\subsection{The Body of the Paper}
	\subsubsection{Type Changes and  Special Characters}
	\subsubsection{Math Equations}
	\paragraph{Inline (In-text) Equations}
	\paragraph{Display Equations}
	\subsubsection{Citations}
	\subsubsection{Tables}
	\subsubsection{Figures}
	\subsubsection{Theorem-like Constructs}
	\subsubsection*{A Caveat for the \TeX\ Expert}
	\subsection{Conclusions}
	\subsection{Acknowledgments}
	\subsection{Additional Authors}
	This section is inserted by \LaTeX; you do not insert it.
	You just add the names and information in the
	\texttt{{\char'134}additionalauthors} command at the start
	of the document.
	\subsection{References}
	Generated by bibtex from your ~.bib file.  Run latex,
	then bibtex, then latex twice (to resolve references)
	to create the ~.bbl file.  Insert that ~.bbl file into
	the .tex source file and comment out
	the command \texttt{{\char'134}thebibliography}.
	% This next section command marks the start of
	% Appendix B, and does not continue the present hierarchy
	\section{More Help for the Hardy}
	The sig-alternate.cls file itself is chock-full of succinct
	and helpful comments.  If you consider yourself a moderately
	experienced to expert user of \LaTeX, you may find reading
	it useful but please remember not to change it.
	%\balancecolumns % GM June 2007
	% That's all folks!
\end{document}

>>>>

	%
	% The following two commands are all you need in the
	% initial runs of your .tex file to
	% produce the bibliography for the citations in your paper.
	\bibliographystyle{abbrv}
	\bibliography{biblio}  
	% You must have a proper ".bib" file
	%  and remember to run:
	% latex bibtex latex latex
	% to resolve all references
	%
	% ACM needs 'a single self-contained file'!
	%
	%APPENDICES are optional
	%\balancecolumns

\end{document}
